Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-07-31 documentation/paper.tex
Use spaces between paragraphs rather than indentation
Created bibliography; added information on fully convolutional networks; updated .gitignore with LaTeX temp files

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}

@@

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}

\addbibresource{paper.bib}

@@

A convolutional neural network was used for analyzing the raw waveform directly, without any preprocessing whatsoever. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle.

For this task, a very deep 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms.

\printbibliography
